%%%%
% Akshay Pramod Teli - Resume
%%%%
\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{setspace}
% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}
% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}
% Colors
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}
% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}
\setlength{\headheight}{14pt}
\addtolength{\topmargin}{-14pt}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{4.1pt}
\raggedbottom
\raggedright
% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}
\renewcommand\labelitemi{-}

%===================%
% Akshay Pramod Teli %
%===================%
\begin{document}
\setstretch{1.1}

  %---------%
  % Heading %
  %---------%
  \documentTitle{Akshay Pramod Teli}{
    \href{tel:+919591461981}{
      \raisebox{-0.05\height} \ +91 9591461981} ~ - ~
    \href{mailto:akshay.teli.001@gmail.com}{
      \raisebox{-0.15\height} \ akshay.teli.001@gmail.com} ~ - ~
    \href{https://www.linkedin.com/in/akshaypramodteli}{
      \raisebox{-0.15\height} \ linkedin.com/in/akshaypramodteli} ~ - ~
    \href{https://akshay-portfolio-a73h.vercel.app/}{
      \raisebox{-0.15\height} \ Portfolio}
  }

  %---------%
  % Summary %
  %---------%
  \tinysection{Summary}
  Senior Product Manager who scaled a lending business from Rs.30 Cr to Rs.100 Cr in disbursals and built an enterprise SaaS platform from 0 to 1 serving global users. 6+ years leading cross-functional teams of up to 27 across payments, fintech, and B2B SaaS - turning ambiguous problem spaces into shipped products with measurable business outcomes.

  %--------%
  % Skills %
  %--------%
  \section{Skills}
  \textbf{Core:} Product Strategy, Roadmapping, PRDs, A/B Testing, GTM Execution, User Research, Stakeholder Management\vspace{4pt}\\
  \textbf{Technical:} SQL, REST APIs, System Design, RBAC, Offline-First Architecture, Webhooks, AI/ML Integration\vspace{4pt}\\
  \textbf{Tools \& Analytics:} Cursor, Claude Code, Lovable, n8n, Supabase, Github, Google Analytics, JIRA, Figma, Amplitude, Metabase, Postman, Confluence\vspace{4pt}\\
  \textbf{Domains:} Payments, Lending, B2B SaaS, Wallets, KYC, ERP, E-commerce, Agri-Tech

  %------------%
  % Experience %
  %------------%
  \section{Experience}
  \headingBf{Senior Product Manager - KJBN Labs Pvt Ltd}{Nov 2024 - Apr 2026}
  \begin{resume_list}
    \item Defined product strategy and led 0-to-1 development of a multi-tenant enterprise SaaS platform, driving architecture decisions and execution from concept through global rollout across multiple business units.
    \item Designed an accounting and ledger system with audit trails and ERP integration, enabling enterprise-grade finance workflows and reducing manual reconciliation effort for customers.
    \item Shipped KYC and contract eligibility automation, cutting manual verification effort by 50\% and accelerating compliance turnaround from days to hours.
    \item Architected role-based access control (RBAC) and configurable workflow engine, enabling secure multi-persona usage and reducing onboarding time for new business units.
    \item Delivered an offline-first mobile application with intelligent sync, achieving 100\% field operations continuity in low-connectivity environments across distributed teams.
  \end{resume_list}
  \vspace{4pt}
  \headingBf{Product Manager - Bijak (B2B Agri-Commerce Platform)}{Feb 2022 - Oct 2024}
  \begin{resume_list}
    \item Scaled the lending business from Rs.30 Cr to over Rs.100 Cr in disbursals by introducing a Loan Management System (LMS) with automated credit decisioning and disbursement workflows.
    \item Built a wallet system with virtual account integration, automating payouts and driving a 23\% increase in DAU and 40\% improvement in user retention on a platform processing 10,000+ monthly trades.
    \item Designed a real-time profitability (XIRR) tracking system providing continuous monitoring of projected vs. actual returns, resulting in a 1.7\% average improvement in trade margins.
    \item Reduced cash transactions by 70\% by introducing digital payment at delivery with a gamified workflow, significantly minimizing payment discrepancies.
    \item Improved gross margins by 4\% through automated flash sale logic that reduced A-grade to B-grade stock transfers by 17\%, directly impacting unit economics.
    \item Led a cross-functional team of 27 (engineering, design, QA, ops) using Agile/Scrum, owning 100+ deployment cycles. Recognized as top performer for 2 consecutive review cycles.
  \end{resume_list}
  \vspace{4pt}
  \headingBf{Co-Founder - VP Mart Pvt Ltd}{Jun 2020 - Jan 2022}
  \begin{resume_list}
    \item Built a hyperlocal marketplace from scratch with dual apps (Customer and Merchant), covering 7+ categories including groceries, restaurants, and services - launched MVP in 3 months.
    \item Owned end-to-end product lifecycle from user research and PRDs to wireframes, development, and GTM strategy, onboarding 41 merchants in the first 4 months.
  \end{resume_list}
  \vspace{4pt}
  \headingBf{Co-Founder - Fangover Food Services Pvt Ltd}{Apr 2019 - Jun 2020}
  \begin{resume_list}
    \item Launched and scaled a food chain to profitability within 6 months by iterating on a data-driven menu strategy (20+ iterations, 60\%+ gross margin) and optimizing CAC to under Rs.100.
    \item Drove 25\% improvement in customer retention through personalized customer experience initiatives and targeted acquisition via Instagram campaigns and affiliate partnerships.
  \end{resume_list}

  %---------------%
  % Side Projects %
  %---------------%
  \section{Side Projects}
  \headingBf{JobMatch - AI Job Fit Scorer}{Personal Project}
  \begin{resume_list}
    \item Built a Chrome extension that scores CV-to-job fit across 7 weighted dimensions and returns an honest 0-100 match score with gap analysis and a clear apply or skip recommendation.
    \item Designed the scoring engine using Claude API with structured JSON output, calibrated to avoid score inflation and flag unrealistic job descriptions.
    \item Deployed the backend API on Railway and built the extension UI using Cursor and Claude Code, shipping end to end without a development team.
  \end{resume_list}
  \vspace{4pt}
  \headingBf{Job Pipeline - Job Application Tracker}{Personal Project}
  \begin{resume_list}
    \item Built a browser sidebar to track job applications, log status updates, and manage follow-ups without leaving the current tab.
    \item Designed and shipped the full stack using Next.js, Supabase for persistence and cross-device sync, and Lovable for rapid UI iteration.
    \item Used Cursor and Claude Code throughout the build for speed and code quality.
  \end{resume_list}

  %-----------%
  % Education %
  %-----------%
  \section{Education}
  \headingBf{PES University, Bangalore}{2015 - 2019}
  \headingIt{B.Tech in Electronics and Communication Engineering}{}
  \vspace{6pt}
  \headingBf{Certifications}{}
  \begin{resume_list}
    \item Certified Scrum Product Owner (CSPO) - Scrum Alliance
    \item Google Data Analytics Professional Certificate - Coursera
  \end{resume_list}

\end{document}
